	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[hidelinks,letterpaper]{deedy-resume-openfont} % Use US Letter paper, change to a4paper for A4 
\usepackage{xcolor}
\hypersetup{
	colorlinks,
	linkcolor={red!50!black},
	citecolor={blue!50!black},
	urlcolor={blue!80!black}
}

\begin{document}
	
	%----------------------------------------------------------------------------------------
	%	TITLE SECTION
	%----------------------------------------------------------------------------------------
	
	\lastupdated % Print the Last Updated text at the top right
	
	\namesection{\Huge Anant}{\Huge Srivastava}{ % Your name
		\urlstyle{same}\url{} \\ % Your website, LinkedIn profile or other web address
		
		\href{mailto:asriva20@asu.edu}{asriva20@asu.edu} | 480.289.0931 % Your contact information
	}
	
	%----------------------------------------------------------------------------------------
	%	LEFT COLUMN
	%----------------------------------------------------------------------------------------
	
	\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page
		
		%------------------------------------------------
		% Education
		%------------------------------------------------
		
		\section{Education} 
		
		\subsection{Arizona State University}
		
		\descript{M.S. in Software Engineering}
		\location{Expected May 2017 | Tempe,AZ \\ Cum. GPA: 3.6/4.0}
		
		
		\sectionsep
		
		\subsection{The LNM Institute of Information Technology}
		
		\descript{B.Tech in Computer Science}
		\location{May 2015 | Rajasthan, India}
		Conc. in Software Engineering \\
		\location{ Cum. GPI: 7.1/10.0 }
		
		\sectionsep
		
		%------------------------------------------------
		
		\subsection{S.t Paul's College}
		
		\location{Grad. May 2010 | Agra, India}
		
		\sectionsep
		
		%------------------------------------------------
		% Links
		%------------------------------------------------
		\vspace{-0.25cm}
		\section{Links} 
		
		LinkedIn:// \href{https://www.linkedin.com/pub/anant-srivastava/54/38/709}{\bf anantsrivastava} \\
		GitHub:// \href{https://github.com/anantsrivastava30}{\bf anantsrivastava30}
		
		\sectionsep
		
		%------------------------------------------------
		% Coursework
		%------------------------------------------------
		\vspace{-0.25cm}
		\section{Coursework}
		
		\subsection{Graduate}
		Human Computer Interaction\\
		Programming Languages \& Compilers\\
		Advanced Computer Graphics\\
		Software Engineering Inception \&
		Elaboration\\
		Advanced Data Structures\\
		Geometric Modelling\\
		Computational Conformal Geometry\\
		Software Design\\
		
		\sectionsep
		
		%------------------------------------------------
		
		\subsection{Undergraduate}
		
		Software Engineering \\
		Operating Systems \\
		Principles of Programming Languages\\
		Design \& Analysis And Algorithms \\
		Computer Organization and Architecture \\
		DataBase Management Systems\\
		Object Oriented Programming (Java)\\
		Data Structures\\
		Information Security and Cyber Laws\\
		Scientific Computing\\
		Number Theory\\
		\sectionsep
		
		%------------------------------------------------
		% Skills
		%------------------------------------------------
		
		\section{Skills}
		
		%\subsection{Programming}
		
		\location{Programming Languages:}
		Python \textbullet{} MATLAB \textbullet{} C \textbullet{} C++ \textbullet{}
		Shell \textbullet{} JavaScript \textbullet{} HTML,CSS,PHP \textbullet{} Mathematica \textbullet{} \LaTeX\ \\ 
		\location{Systems \& IDEs}
		MATLAB \textbullet{} Xilinx \textbullet{} Visual Studio \textbullet{} Unix \textbullet{} Linux \textbullet{} MySQL
		Inkspace
		\sectionsep
		
		%----------------------------------------------------------------------------------------
		
	\end{minipage} % The end of the left column
	\hfill
	%
	%----------------------------------------------------------------------------------------
	%	RIGHT COLUMN
	%----------------------------------------------------------------------------------------
	%
	\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
		%------------------------------------------------
		% Summary
		%------------------------------------------------
		
		\section{Summary}
		\footnotesize
		Software Engineering graduate with MS Thesis in "3D - Patch Based Machine Learning Systems for Alzheimer's Disease classification via $^{18}$FDGPET ~Analysis" looking for an entry level opportunity to enhance technical and interpersonal skills. Experienced in machine learning, software engineering and data analysis. Passionate about mathematics and deep learning. Programming skillset includes Python, C, Java and MATLAB. Quick learner with acute analytical skills and have comprehensive knowledge of \textbullet{Software Engineering} \textbullet{Data analysis and Machine Learning} \textbullet{Computer Graphics}
		
		
		%------------------------------------------------
		% Experience
		%------------------------------------------------
		\section{Experience / Research}
		
		\runsubsection{\normalsize A.S.U}
		\descript{\normalsize | Graduate Research Assistant , Geometric Systems Lab}
		
		\location{May 2016 - June 2016 | Tempe, AZ}
		\footnotesize
		Preprocessed raw P.E.T scans and analyzed them based on different stages in disease proression. A fair bit
		has been done in the study of Alzheimer’s and structural MRI. While working in GSL I  found and classified relevant information in P.E.T. Scans. We succeeded in classifiying most of the stages. Publications submitted.
		\sectionsep
		
		\runsubsection{\normalsize N.C.A.E.R}
		\descript{\normalsize | Project Intern, Science Department}
		
		\location{June 2013 - July 2013 | New Delhi, India}
		\footnotesize
		Worked under the project NSDI (National Spatial Data Infrastructure), which involved conversion of
		original dataset in different formats for efficient utilization, creation of metadata and uploading it to the
		NSDI web portal.
		\sectionsep
		
		%------------------------------------------------
		% Projects
		%------------------------------------------------
		\vspace{-0.25cm}
		\section{Academic Projects}
		
		\runsubsection{\normalsize Socially Expressive Physical Agent}
		\descript{\normalsize | Tools Used : TOOLS : PSOC Creator 4.0, 3D PRINTER, WIRES AND MOTORS}
		
		\location{August 2016 - December 2016 \& January 2017 - May 2017 | Tempe, AZ}
		\footnotesize Built a Functional Automation’s Head using parts ordered from amazon. We 3D printed the head
		structure and designed and programmed it to show emotions. Continued the project for a more robust
		design
		
		\sectionsep
		
		\runsubsection{\normalsize Flash Programming Language}
		\descript{\normalsize | Tools Used : - Java, C, FLEX (2.6.0), BISON (GNU 3.0.4)}
		
		\location{January 2016 - May 2016 | Tempe, AZ}
		\footnotesize Developed Flash 5.0 which is a Mordern block structured, Strongly Typed, Procedural Programming Language\\
		Youtube Video Link: \href{https://www.youtube.com/watch?v=cSMFHlU0nXk}{\bf CompilerRuntime Flash 5.0} \\
		Github Link : \href{https://github.com/anantsrivastava30/CompilerRuntime}{\bf CompilerRuntime Flash 5.0}  
		
		\sectionsep
		
		\runsubsection{\normalsize Implementing binary Loop subdivision surfaces}
		\descript{\normalsize | Tools : OpenGl, MeshLab, VisualStudio, C++}
		\location{September 2015 - October 2015 | Tempe, AZ}
		\footnotesize Testing data: 1) Utah teapot model 2) Stanford bunny model. The objective of this project is to create sculptured smooth suraces.
		
		\sectionsep
		
		\runsubsection{\normalsize SCORE Project: DRisk, A Dynamically Configurable Risk Game}
		\descript{\normalsize | Tools : Javascript, Scrum (Agile), }
		\location{August 2015 - December 2015 | Tempe, AZ}
		\footnotesize Risk is a turn-based board game, in which 2 to 6 players fight over the occupation of 42 territories in a political map, trying to achieve a secret mission that generally requires the control of the territories in the map. Github Link : \href{https://github.com/ser515asu/DRisk-Team-MASCS/tree/master/riskmap}{\bf D-Risk}  
		
		\sectionsep
		
		\runsubsection{\normalsize Non-intrusive virtual Management using LIBVIRT}
		\descript{\normalsize | Tools USed: LIBVIRT API, C++ ,VMware.}
		\location{Jan 2013 - May 2013 | Jaipur, India}
		\footnotesize The objective of the research was to devise operating system techniques to generalise virtualization on an operating system. The libvirt management API provides tool for the same. We simplified a uniform management system by a layer abstracting from these hypervisor interfaces.
		
		\sectionsep
		
		%------------------------------------------------
		
		
		
		
		%------------------------------------------------
		% Awards
		%------------------------------------------------
		\vspace{-0.25cm}
		\section{Publications \& Awards} 
		
		\begin{tabular}{rll}
			2017	& 2 Poster publications at AAC (Arizona Alzheimer's Consortium) for Machine \& Deep Learning  \\ 
			2013	& Co-Ordinator- Social Awareness Club (Nukkar-Mandli) at LNMIIT\\
			2012	 & 1\textsuperscript{st}- Inter-college Robo Race (Plinth) at LNMIIT\\
			2011	& Active participant Leprosy Eradication Drive
		\end{tabular}
		
		%----------------------------------------------------------------------------------------
		
	\end{minipage} % The end of the right column
	
	%----------------------------------------------------------------------------------------
	%	SECOND PAGE (EXAMPLE)
	%----------------------------------------------------------------------------------------
	
	%\newpage % Start a new page
	
	%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page
	
	%\section{Example Section}
	
	%\end{minipage} % The end of the left column
	%\hfill
	%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
	
	%\section{Example Section 2}
	
	%\end{minipage} % The end of the right column
	
	%----------------------------------------------------------------------------------------
	
\end{document}